Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-06-01 analysis/preregistration_template.Rmd
Update analysis/preregistration_template.Rmd
Add new item number and heading after HF's suggestion to split 2.4.5

*Describe how you will determine how reliable the data is for the given purpose. Ideally, model input data should be internally consistent across temporal and spatial scales and resolutions, and appropriate to the problem at hand [@Mahmoud2009].*

*Document any issues with data reliability. This is important because data quality and ecological relevance might be constrained by measurement error, inappropriate experimental design, and heterogeneity and variability inherent in ecological systems [@Grimm:2014es].*

>>>>

*Describe how you will determine how reliable the data is for the given purpose. Ideally, model input data should be internally consistent across temporal and spatial scales and resolutions, and appropriate to the problem at hand [@Mahmoud2009].* 
### 2.4.5 Data Evaluation: Data reliability reporting
*Document any issues with data reliability. This is important because data quality and ecological relevance might be constrained by measurement error, inappropriate experimental design, and heterogeneity and variability inherent in ecological systems [@Grimm:2014es].*
